\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2017-01-12 report/paper.tex
Added some figure texts

When the application starts, the water is represented as set of spheres where every sphere has the properties of a particle. The initial state is illustrated Figure~\ref{fig:res1}. The water is affected by a gravity which induce a falling motion, illustrated in Figure~\ref{fig:res2}.

@@

Since the water aims to be in the state of rest, the motion will decrease over time which is illustrated in Figure~\ref{fig:res3}.
\begin{figure}[h!]
    \includegraphics[width=\linewidth]{img/frame0500.png}
    \caption{caption}
    \label{fig:res3}
\end{figure}

To be able to simulate how outer forces affect the water, we implemented a feature where the user is able to change the direction of the force. The result when applying a force from right to left on the water and then letting only the gravity affect it is shown in Figure~\ref{fig:res4}.
\begin{figure}[h!]
    \includegraphics[width=\linewidth]{img/frame0882.png}
    \caption{caption}
    \label{fig:res4}
\end{figure}

>>>>

	When the application starts, the water is represented as set of spheres where every sphere has the properties of a particle.
	The initial state is illustrated in Figure~\ref{fig:res1}
	The water is affected by a gravity which induce a falling motion, illustrated in Figure~\ref{fig:res2}.

@@

	Since the water aims to be in the state of rest, the motion will decrease over time which is illustrated in Figure~\ref{fig:res3}.
	\begin{figure}[h!]
		\includegraphics[width=\linewidth]{img/frame0500.png}
		\caption{The water is calm with some motion.}
		\label{fig:res3}
	\end{figure}

	To be able to simulate how outer forces affect the water, we implemented a feature where the user is able to change the direction of the force
	The result when applying a force from right to left on the water and then letting only the gravity affect it is shown in Figure~\ref{fig:res4}.

	\begin{figure}[h!]
		\includegraphics[width=\linewidth]{img/frame0882.png}
		\caption{The water after an applied right to left motion followed by gravity as the only outer force.}
		\label{fig:res4}
	\end{figure}
